Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-11-07 WSSSPE4_report/survey_details.tex

\begin{itemize}
\item Concrete reports about best practices
\item considerations of software licensing, build systems, delivery (source vs binary vs whatever) - but of course these are "later" issues... first one needs the software to not be hidden, to have version control, have a README, etc.
\item Container sustainability practices
\item education, training interns
\item Explicit follow-up at WSSSPE5 on all the activities that were created at WSSPE4.  These should be at least lightning talks, perhaps with their own session.
\item financial models for sustaining software
\item Frameworks for building software
\item have a short beginning presentation for each working group and a short ending presentation
\item How software development training can be adapted to different disciplines beyond STEM
\item How to low the barrier for non-tech heavy researchers to follow best software practices.
\item I would like to have more discussions about research, if people can share their research or some of the interesting projects that they're working on, this will help in knowing the problems in sustaining software.
\item I would like to learn more about sustainability issues in industry.
\item I would like to see more grounded advice and less blue-sky thinking. A lot of stuff in the talks was 'this would be nice' but there were not enough talks that were directly applicable to day-to-day programming.
\item Like to see more examples from the real world.  
\item Mechanisms of improving software reusability
\item More concrete projects, concrete possibilities and showcases for collaboration with results
\item Practical ways of achieving some of the goals rather than the discussion of more attempts on the writing of white papers
\item Reproducibility through containerization (I guess there is another list of best practices needed there)
\item RSE award, organizational questions regarding setting up RSE teams within universities
\item Software testing
\item Some theory on what makes for sustainable software, which is not the same as best practice for research software engineering. If this had been talked about before then consider that 80\% of us were new.
\item Specific scientific software sustainability factors
\item Testing methods that work. Ways of promoting organizational change.
\item The progress of our current project.
\item The use of scientific software at different stages of research / work 
\item We discussed scientific software. Should we also discuss software FOR scientists (like Dan's google scholar replacement)?
\end{itemize}

@@

\begin{itemize}
\item A bit less fly by night scheduling though things worked out just fine.  
\item A lot of the speakers just seemed to be there either to plug their own projects (e.g. Hydroshare, BioDynaMo) or spent the majority of their talk waffling (e.g. Manifesto for Personal Responsibility in the Engineering of Academic Software). Also, the icebreakers were not very useful.
\item A single room for the duration of the meeting. (Particular to this WSSSPE4, the "collaboratory" room with the monitors, was actually perfect for the full meeting.)
\item Allotting more time for questions \& discussions in between talks
\item close to perfect workshop - if I would change one thing that give more time for discussions
\item consistency of participants
\item felt locked in to the breakout group, not sure if that was intended or not
\item Finding rooms a bit confusing at the meeting outset
\item Having more time for the demos.
\item Having more time to discuss some of the talks
\item I was disappointed in the fruit plate because it only had melon.
\item I would like to be able to ask questions after talks. By the time we can discuss the talks, I've forgotten what I wanted to say
\item Identify a local pub/restaurant/cafe to which people can head afterwards for casual meetup for dinner/drinks/discussion/whatever
\item If feedback to people's projects and lighting talks etc is posted online, then we would have also benefits from those thoughts
\item It was a great event overall I feel like if we can bring some real life project integration with best practices that will be helpful 
\item it would be great to see some specific case studies/success stories
\item Keep the online agenda up to date. Better air-conditioning.
\item Less talks
\item more time for discussion and working groups
\item not sure, it looks great to me. I would like to see in plenary the perspective from closed software and open source software (for cross-fertilization)
\item Some longer talks that do deeper dives.  Good that the parallel track idea was abandoned so we could hear all talks.
\item The identification of what RSE and RS are, especially for newcomers
\item The keynote address could have been better targeted for this community beforehand.
\item The workshop was great!!!
\item There is lots of vision here, so we need to put more effort in our project to move forward.
\item Think about a little more planning on the BOF Dinners to make it easier to get groups together. Maybe a Google doc to encourage it etc.
\item To have a few speakers (2-3) that talk about concrete scientific software, showing the simulations and talking about their scientific results, and why they chose the software they did (as compared to other available ones)
\item Try and add some extra Q\&A time after talks (unless that'd mean less talks)
\item We could have additional time to work in working groups
\item WSSPE vision prior to start would have helped
\end{itemize}

@@

\begin{itemize}
\item "Citations / CodeMeta"  and  "Software Practices White Paper"
\item Best Practices White Paper and Best Practices Undergraduate Course
\item CodeMeta
\item CodeMeta
\item CodeMeta
\item CodeMeta, but I also supplied information to other working groups -- mostly connections to others -- that I hope will be of assistance.
\item Continuous CI for research software on uncommon hardware
\item Continuous Integration
\item Continuous integration for research software; Testing of scientific software
\item Curriculum for an undergraduate course on software best practices for domain scientists
\item Domain Specific Undergraduate Courses on Best Practices for Software Development
\item Domain Specific Undergraduate Courses on Best Practices for Software Development AND International Collaborations between institutions.
\item integration of software testing through Debian 
\item Meaningful Metrics for Scientific Software
\item Meaningful Metrics in Software
\item metadata
\item multiple
\item Open Research Index, Metrics, Social Science, and maybe others
\item Prototypes
\item research software studies
\item Scientific Software Prototyping Infrastructure (S2PI), WG-Best-Practices
\item Setting up Software Sustainability Alliance
\item Software Sustainability Alliance
\item Software Sustainability Alliance; Metrics; White Paper
\item sustainability metrics; best practices
\item Sustainable Software Alliance
\item Sustainable Software Alliance
\item Tenure Letters
\item Testing in Sciences
\item Testing in Scientific Software
\item Verify Best Practices and Metrics for Sustainable Software
\item Verify Best Practices Case Studies
\item White Paper WG, Open Research Index WG
\end{itemize}

@@

\item This was an excellent mix of people, timed/structured activities, and untimed events. I had the opportunity to talk to numerous people about projects, issues, and ways to improve science/scientific software, and leave with many new ideas and possible collaborations/cooperative efforts with complementary projects. The working groups activities were excellent, a good mix of projects, and I saw a lot of progress on several I'm very interested in. (Please group this survey with my earlier one; I hit "end" too soon on the other! Thanks!)

>>>>

\begin{itemize}
\item Concrete reports about best practices
\item considerations of software licensing, build systems, delivery (source vs binary vs whatever) - but of course these are ``later'' issues... first one needs the software to not be hidden, to have version control, have a README, etc.
\item Container sustainability practices
\item education, training interns
\item Explicit follow-up at WSSSPE5 on all the activities that were created at WSSPE4.  These should be at least lightning talks, perhaps with their own session.
\item financial models for sustaining software
\item Frameworks for building software
\item have a short beginning presentation for each working group and a short ending presentation
\item How software development training can be adapted to different disciplines beyond STEM
\item How to low the barrier for non-tech heavy researchers to follow best software practices.
\item I would like to have more discussions about research, if people can share their research or some of the interesting projects that they're working on, this will help in knowing the problems in sustaining software.
\item I would like to learn more about sustainability issues in industry.
\item I would like to see more grounded advice and less blue-sky thinking. A lot of stuff in the talks was `this would be nice' but there were not enough talks that were directly applicable to day-to-day programming.
\item Like to see more examples from the real world.  
\item Mechanisms of improving software reusability
\item More concrete projects, concrete possibilities and showcases for collaboration with results
\item Practical ways of achieving some of the goals rather than the discussion of more attempts on the writing of white papers
\item Reproducibility through containerization (I guess there is another list of best practices needed there)
\item RSE award, organizational questions regarding setting up RSE teams within universities
\item Software testing
\item Some theory on what makes for sustainable software, which is not the same as best practice for research software engineering. If this had been talked about before then consider that 80\% of us were new.
\item Specific scientific software sustainability factors
\item Testing methods that work. Ways of promoting organizational change.
\item The progress of our current project.
\item The use of scientific software at different stages of research / work 
\item We discussed scientific software. Should we also discuss software FOR scientists (like Dan's google scholar replacement)?
\end{itemize}

@@

\begin{itemize}
\item A bit less fly by night scheduling though things worked out just fine.  
\item A lot of the speakers just seemed to be there either to plug their own projects (e.g. Hydroshare, BioDynaMo) or spent the majority of their talk waffling (e.g. Manifesto for Personal Responsibility in the Engineering of Academic Software). Also, the icebreakers were not very useful.
\item A single room for the duration of the meeting. (Particular to this WSSSPE4, the ``collaboratory'' room with the monitors, was actually perfect for the full meeting.)
\item Allotting more time for questions \& discussions in between talks
\item close to perfect workshop - if I would change one thing that give more time for discussions
\item consistency of participants
\item felt locked in to the breakout group, not sure if that was intended or not
\item Finding rooms a bit confusing at the meeting outset
\item Having more time for the demos.
\item Having more time to discuss some of the talks
\item I was disappointed in the fruit plate because it only had melon.
\item I would like to be able to ask questions after talks. By the time we can discuss the talks, I've forgotten what I wanted to say
\item Identify a local pub/restaurant/cafe to which people can head afterwards for casual meetup for dinner/drinks/discussion/whatever
\item If feedback to people's projects and lighting talks etc is posted online, then we would have also benefits from those thoughts
\item It was a great event overall I feel like if we can bring some real life project integration with best practices that will be helpful 
\item it would be great to see some specific case studies/success stories
\item Keep the online agenda up to date. Better air-conditioning.
\item Less talks
\item more time for discussion and working groups
\item not sure, it looks great to me. I would like to see in plenary the perspective from closed software and open source software (for cross-fertilization)
\item Some longer talks that do deeper dives.  Good that the parallel track idea was abandoned so we could hear all talks.
\item The identification of what RSE and RS are, especially for newcomers
\item The keynote address could have been better targeted for this community beforehand.
\item The workshop was great!!!
\item There is lots of vision here, so we need to put more effort in our project to move forward.
\item Think about a little more planning on the BOF Dinners to make it easier to get groups together. Maybe a Google doc to encourage it etc.
\item To have a few speakers (2-3) that talk about concrete scientific software, showing the simulations and talking about their scientific results, and why they chose the software they did (as compared to other available ones)
\item Try and add some extra Q\&A time after talks (unless that'd mean less talks)
\item We could have additional time to work in working groups
\item WSSPE vision prior to start would have helped
\end{itemize}

@@

\begin{itemize}
\item ``Citations / CodeMeta''  and  ``Software Practices White Paper''
\item Best Practices White Paper and Best Practices Undergraduate Course
\item CodeMeta
\item CodeMeta
\item CodeMeta
\item CodeMeta, but I also supplied information to other working groups -- mostly connections to others -- that I hope will be of assistance.
\item Continuous CI for research software on uncommon hardware
\item Continuous Integration
\item Continuous integration for research software; Testing of scientific software
\item Curriculum for an undergraduate course on software best practices for domain scientists
\item Domain Specific Undergraduate Courses on Best Practices for Software Development
\item Domain Specific Undergraduate Courses on Best Practices for Software Development AND International Collaborations between institutions.
\item integration of software testing through Debian 
\item Meaningful Metrics for Scientific Software
\item Meaningful Metrics in Software
\item metadata
\item multiple
\item Open Research Index, Metrics, Social Science, and maybe others
\item Prototypes
\item research software studies
\item Scientific Software Prototyping Infrastructure (S2PI), WG-Best-Practices
\item Setting up Software Sustainability Alliance
\item Software Sustainability Alliance
\item Software Sustainability Alliance; Metrics; White Paper
\item sustainability metrics; best practices
\item Sustainable Software Alliance
\item Sustainable Software Alliance
\item Tenure Letters
\item Testing in Sciences
\item Testing in Scientific Software
\item Verify Best Practices and Metrics for Sustainable Software
\item Verify Best Practices Case Studies
\item White Paper WG, Open Research Index WG
\end{itemize}

@@

\item This was an excellent mix of people, timed/structured activities, and untimed events. I had the opportunity to talk to numerous people about projects, issues, and ways to improve science/scientific software, and leave with many new ideas and possible collaborations/cooperative efforts with complementary projects. The working groups activities were excellent, a good mix of projects, and I saw a lot of progress on several I'm very interested in. (Please group this survey with my earlier one; I hit ``end'' too soon on the other! Thanks!)

### 2016-11-07 WSSSPE4_report/wg_codemeta.tex

Because of the work done at WSSSPE4, the CodeMeta project README file\citep{\url{https://github.com/codemeta/codemeta/blob/master/README.md}} was greatly expanded to include a description of the project that is geared to those with little or no prior knowledge of the project and including a list of contributors, information on how one can get involved, a bit of the project history and who is managing the project, and links to additional information.

>>>>

Because of the work done at WSSSPE4, the CodeMeta project README file\footnote{\url{https://github.com/codemeta/codemeta/blob/master/README.md}} was greatly expanded to include a description of the project that is geared to those with little or no prior knowledge of the project and including a list of contributors, information on how one can get involved, a bit of the project history and who is managing the project, and links to additional information.
